Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-11 figures/metabolism.tex
合并各个子小节，插入了一张service 剖析图

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (add) {New Machine}; & \node (machinein) [square] {Arrival Restrictor}; & & & & & & &\\
\node (origin) {Origin Scarcity}; & & \node (compare) [circle] {\Large$\times$}; & & \node (scarcity) [square] {Machine Scarcity}; & \node (metabolism) [square] {Metabolism Module}; &\node (node) [coord] {}; &\node (end) [coord] {};\\
\node (task) {New Task}; & \node (p1) [coord] {};& & \node (p2) [coord] {}; & \node (reduce) [square] {Eliminate Machine}; & & & & \\
& & \node (tf) {Task Finish}; &  & & & & &\\
};
\path (add) edge[->] (machinein) (machinein.east) edge[->] (compare) (compare) edge[->] (scarcity) (scarcity) edge[->] (metabolism);
\path (origin) edge[->] (compare);
\path (tf) edge[->] (compare);
\path (reduce) edge (p2) (p2) edge[->] (compare);
\draw [->] (metabolism) -- (end) ;
\draw [->]  (task) -- (p1) -- (compare);
\path (node) edge[->,skip loop=5.5em] (machinein);
\draw [->] (node) |- (reduce);
\path (machinein.east) to node [near end,yshift=0.5em,xshift=0.5em] {$-$} (compare);
\path (tf) to node [near end,xshift=0.5em] {$-$} (compare);
\path (p1) to node [near end,xshift=0.8em] {$+$} (compare);
\path (p2) to node [near end,xshift=0.5em,yshift=0.3em] {$+$} (compare);
\path (node) to node [near end,xshift=2em,yshift=0.6em] {Decision value} (end);
\end{tikzpicture}

>>>>

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
&&&&& & & \node (machinein) [square] {Arrival Restrictor}; & \node (add) {};  &  & &\\
&&&&&&&&&&&\\
&&&&&&&&&&&\\
& & && &\node (origin2) {};  & \node (compare2) [circle] {\Large$\times$}; &  \node (scarcity) [square] {Machine Scarcity}; & \node (metabolism) [square] {Metabolism Module}; &\node (node2) [coord] {}; &\node (end2) [coord] {};\\
&&&&&\node (task) {}; &  & \node (reduce) [square] {Eliminate Machine}; &  & & &\\
&&&&& &  &  & & & & &&  \\
};
\path (add) edge[->] (machinein) (machinein.west) edge[->] (compare2) (compare2) edge[->] (scarcity) (scarcity) edge[->] (metabolism);
\path (origin2) edge[->] (compare2);
% \path (tf) edge[->] (compare2);
\path (reduce.west)  edge[->] (compare2);
\draw [->] (metabolism) -- (end2) ;
\draw [->]  (task) -- (compare2);
\path (node2) edge[->,skip loop=2.2em] (machinein);
\draw [->] (node2) |- (reduce);
\path (machinein.west) to node [near end,yshift=-0.5em,xshift=0.5em] {$-$} (compare2);
% \path (tf) to node [near end,xshift=0.5em] {$-$} (compare2);
\path (task) to node [near end,xshift=0.8em] {$+$} (compare2);
\path (reduce) to node [near end,xshift=-0.6em,yshift=-0.8em] {$+$} (compare2);
\path (node2) to node [near end,xshift=2em,yshift=0.6em] {Decision var.} (end2);
\path (add) to node [near start, xshift=7em] {New Registered Resource}(machinein) (origin2) to node [near start,xshift=-4em]{Origin Scarcity}(compare2) (task.east) to node [near start,xshift=-3em]{New Task} (compare2);
\end{tikzpicture}

### 2016-09-11 figures/outsource.tex
合并各个子小节，插入了一张service 剖析图

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
\node (origin) {Origin Length} ; & \node (compare) [circle] {\Large$\times$}; & & \node (length) [square] {Queue Length} ; & \node (outsource) [square] {Outsourcing Module} ; & \node (node) [coord] {} ; & \node (end) [coord] {}; \\
& & \node (p1) [coord] {} ; & \node	(out) [square] {Outsource Task} ; & & & \\
& \node (tf) {Task Finish}; & & & & &\\
};
\path (origin) edge[->] (compare) (tf) edge[->] (compare) (compare) edge[->] (length) (length) edge[->] (outsource) (outsource) edge[->] (end);
\path (out) edge (p1) (p1) edge[->] (compare);
\draw [->] (node) |- (out) ;
\path (tf) to node [near end,xshift=0.3em] {$+$} (compare) (p1) to node [near end,xshift=0.5em] {$-$} (compare) (outsource) to node [yshift=0.7em,xshift = 1.5em] {Decision value} (end);
\end{tikzpicture}

>>>>

% !TEX root = flow_head.tex
\begin{tikzpicture}[node distance=5mm and 5mm,
square/.style={
% The shape:
rectangle,
draw=black,
minimum size=2.9em,
text width=5em,
text centered
},
coord/.style={
coordinate,
% on chain,
% on grid,
% node distance=6mm and 25mm
},
circle/.style={
rectangle,minimum size=2em,rounded corners=1em,
draw=black
},
skip loop/.style={to path={-- ++(0,#1) -| (\tikztotarget)}}
]
\matrix[row sep=0.5em,column sep=2em] {
% First row:
& & &   \node	(out) [square] {Outsource Task} ; &  \node (originl) {Origin Length} ; & \\
\node (end1) [coord] {}; & \node (node1) [coord] {} ; & \node (outsource) [square] {Outsourcing Module} ; &\node (length) [square] {Queue Length} ; & \node (compare1) [circle] {\Large$\times$};  & \\
&  & &  & &\\
};
\path (originl) edge[->] (compare1) (compare1) edge[->] (length) (length) edge[->] (outsource) (outsource) edge[->] (end1);
\path (out.east) edge[->] (compare1);
\draw [->] (node1) |- (out) ;
\path (out) to node [near end,xshift=0.5em,yshift=0.7em] {$-$} (compare1) (outsource) to node [near end,yshift=-0.7em,xshift = -0.7em] {Decision var.} (end1);
\end{tikzpicture}

### 2016-09-11 figures/scheduleChart.tex
合并各个子小节，插入了一张service 剖析图

\draw (7.5cm,-7mm) node{$r_4$, initial capacity = 10, type = 3};
\draw[yshift=6.5cm] (7.5cm,-7mm) node{$r_3$, initial capacity = 10, type = 3};
\draw[yshift=13cm] (7.5cm,-7mm) node{$r_2$, initial capacity = 10, type = 2};
\draw[yshift=19.5cm] (7.5cm,-7mm) node{$r_1$, initial capacity = 10, type = 1};

\fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (6cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm)  (4.5cm,1.6cm) node{$t_3$} (7cm,4.5cm) node{$sc_2$} (10.5cm,1.8cm) node{$t_2$} (2cm,2.25cm) node{$t_4$} (4.5cm,3.25cm) node{$t_5$};
\draw[dotted,yshift=19.5cm] (0,5cm) -- (7cm,5cm) (3cm,4cm) -- (15cm,4cm) (7cm,0) -- (7cm,5cm) (8cm,4cm) -- (8cm,3.5cm);
\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,4cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,3.5cm)  (3.5cm,1.35cm) node{$t_1$} (7.5cm,4.5cm) node{$sc_2$} (10.5cm, 1.35cm) node{$t_2$}  (2cm,3cm) node{$t_4$};
\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (0,4cm) -- (15cm,4cm) (7cm,5cm) -- (7cm,0) (8cm,5cm) -- (8cm,0);
\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,2cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm) (3.5cm,1.85cm) node{$t_1$} (7.5cm,3.5cm) node{$sc_2$} (4.5cm,4.25cm) node{$t_5$};
\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,2cm) -- (15cm,2cm) (8cm,0) -- (8cm,2cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,3cm) (4.5cm, 1.35cm) node {$t_3$} (0.5cm,4.3cm) node{$sc_1$} (10.5cm,1.8cm) node{$t_2$} (2cm,1.5cm) node{$t_4$};
\draw[dotted] (0,3.5cm) -- (15cm,3.5cm) (1cm,0) -- (1cm,3.5cm);
\end{tikzpicture}

>>>>

\draw[yshift=6.5cm] (7.5cm,-11mm) node{$mr_4$, $C_{4,0} = 10$, $P(mr_4) = 3$};
\draw[yshift=13cm] (7.5cm,-11mm) node{$mr_3$, $C_{3,0} = 10$, $P(mr_3) = 3$};
\draw[yshift=19.5cm] (7.5cm,-11mm) node{$mr_2$, $C_{2,0} = 10$, $P(mr_2) = 2$};
\draw[yshift=26cm] (7.5cm,-11mm) node{$mr_1$, $C_{1,0} = 10$, $P(mr_1) = 1$};

% \fill[blue!20!,yshift=19.5cm] (6cm,4cm) rectangle (7cm,5cm);
\draw[yshift=19.5cm] (3cm,0) rectangle (6cm,3cm) (8cm,0) rectangle (13cm,3.5cm) (1cm,0) rectangle (3cm,4.5cm) (3cm,3cm) rectangle (6cm,3.5cm) (0,4.5cm) rectangle (1cm,5cm)  (4.5cm,1.6cm) node{$job_3$} (10.5cm,1.8cm) node{$job_2$} (2cm,2.25cm) node{$job_4$} (4.5cm,3.25cm) node{$job_5$} (0.5cm,4.75cm) node{$job_6$};
\draw[dotted,yshift=19.5cm] (3cm,4.5cm) -- +(12cm,0);

\draw[yshift=13cm] (0,0) rectangle (7cm,2.5cm) (7cm,2.5cm) rectangle (8cm,5cm) (8cm,0) rectangle (13cm,2.5cm) (1cm,2.5cm) rectangle (3cm,4.5cm)  (3.5cm,1.35cm) node{$job_1$} (7.5cm,3.75cm) node{$job_7$} (10.5cm, 1.35cm) node{$job_2$}  (2cm,3.5cm) node{$job_4$};
\draw[dotted,yshift=13cm] (0,5cm) -- (7cm,5cm) (8cm,2.5cm) -- (15cm,2.5cm);

\draw[yshift=6.5cm] (0,0) rectangle (7cm,3.5cm) (7cm,3cm) rectangle (8cm,5cm) (3cm,3.5cm) rectangle (6cm,5cm)  (8cm,0) rectangle (13cm,2.5cm) (3.5cm,1.85cm) node{$job_1$} (7.5cm,4cm) node{$job_7$} (4.5cm,4.25cm) node{$job_5$} (10.5cm,1.25cm) node{$job_2$};
\draw[dotted,yshift=6.5cm] (0,5cm) -- (7cm,5cm) (8cm,3cm) -- (15cm,3cm) (8cm,3cm) -- (8cm,2.5cm);

\fill[blue!20!] (6cm,2cm) rectangle (7cm,3.5cm);
\draw (0,3.5cm) rectangle (1cm,5cm) (3cm,0) rectangle (6cm,2.5cm)  (1cm,0) rectangle (3cm,3cm) (6cm,2cm) rectangle (8cm,3.5cm) (4.5cm, 1.35cm) node {$job_3$} (0.5cm,4.3cm) node{$job_6$}  (2cm,1.5cm) node{$job_4$} (7cm,2.75cm) node{$job_7$};
\draw[dotted] (0,3.5cm) -- (6cm,3.5cm) (1cm,0) -- (1cm,3.5cm) (8cm,2cm) -- (15cm,2cm) (7cm,2cm) -- +(0,1.5cm) (8cm,2cm) -- (8cm,0);
\end{tikzpicture}
